### 2016-07-29 text/formal_background.tex
Replace DSLTrans section with Frankenstein from different sources.

\subsection{DSLTrans Constructs}
\label{sec:DSLTrans_formal}

This section will detail the abstract syntax of the constructs involved in a DSLTrans transformation.

As discussed in Section~\ref{subsec:DSLTrans_syntax}, DSLTrans transformations are composed of rules arranged in layers.

\subsubsection{Similar Structures}

Note that in the definitions that follow, in this section and others, that we define structures which are very similar in composition, which each containing two or three typed graphs, as well as a link component. This similarity is essential to our technique, as we will define morphisms between the various components of these constructions, which vary depending on the particular structure under examination.

While this composition of typed graph approach is preferred by the authors due to its reflection in our prover implementation, some readers may disagree. In this case, note that it is equivalent to think of these structures as one large typed graph annotated by the component it originates from, with appropriate projections for selecting relevant portions.

\subsubsection*{DSLTrans Transformation Rule}

A transformation rule is the elemental block of a DSLTrans transformation. Several transformation rules can be observed in the Police Station transformation in \cref{fig:dsltransformation}.

A transformation rule includes a non-empty match pattern and a non-empty apply pattern. This is also known in the model transformation literature as a rule's \emph{left hand side} and \emph{right hand side}. As described in Section 3.4 or Section 2, which the match graph elements are found in the input model, then the apply graph elements are produced in the output model.

A match pattern can include indirect links that are used to transitively match containment relations in a model. The apply pattern of a rule always contains at least one apply element that is not connected to a backward link or an edge, meaning in practice that a rule will always produce something and not only match. An apply pattern does not include indirect links as it is used only for the construction of parts of instances of a metamodel.

A rule may also contain a negative application condition (NAC) which if matched over the target graph prevents application of the rule.

A transformation rule also includes backward links, as informally introduced in \cref{subsec:DSLTrans_constructs}. As described in that section, backward links define dependencies between rules. \bentley{Expand}

\begin{definition}{DSLTrans Transformation Rule\\}
\label{def:transformation_rule}

A DSLTrans transformation rule is a four-tuple $\big\langle \mathit{NAC}$, $\mathit{Match}$, $\mathit{Apply}$, $\mathit{backward}\big\rangle$, where:

\begin{itemize}
\item $\mathit{NAC}$, $\mathit{Match}, \mathit{Apply} \in \textsc{TG}$
\item $\mathit{Match}$ and $\mathit{Apply} $ are non-empty and are disjoint
\item $\mathit{NAC}$ may be an empty graph, and is disjoint from both $\mathit{Match}$ and $\mathit{Apply} $

\end{itemize}

Note that when we require an element of the $\mathit{Match}$, $\mathit{Apply}$, or $\mathit{NAC}$ graphs, such as the vertices, we will index the required element. For example, the vertices for the \textit{Match} graph will be $V_{\textit{Match}}$.

\begin{itemize}
\item $\mathit{backward} = \{E_{back}, (s_{back}, t_{back})\}$
\item $E_{back}$ contains the backward links
\begin{itemize}
\item $E_{back} $ is disjoint from $E_{Match}$,  $E_{Apply}$, and $E_{NAC}$
\end{itemize}
\item $(s_{back}, t_{back})$ is a pair of functions $s_{back}: E_{back}\rightarrow V_{\textit{Apply}}$ and $t_{back}: E_{back}\rightarrow V_{\textit{Match}}$ that respectively provide the pattern and target vertices for each backward link
\begin{itemize}
\item Note the source of backward links is a vertex in $V_{\textit{Apply}}$ while the target is a vertex in $V_{\textit{Match}}$
\end{itemize}
\end{itemize}

\textsc{Rules} is the set of all rules.

We additionally impose that for the well-formedness of a DSLTrans rule, there always exists an element or edge to be created in the \textit{Apply} graph to be created. That is, either there are edges to be created in the \textit{Apply} graph, or there is a vertex in the \textit{Apply} graph that is not the source of a backward link.

\begin{itemize}
\item $E_{\textit{Apply}} \neq \emptyset \lor$
\item $ \exists v \in V_{\textit{Apply}} | \big\{\forall e \in E_{back}: s_{back}(e) \neq v \big\}$
\end{itemize}

@@

We also note that we will resolve the binding of all morphisms at the appropriate time, and ensure that they are consistent. \bentley{FIXFIX}

\subsubsection*{DSLTrans Layer and Transformation}

\cref{def:layer} and \cref{def:transformation} formalise the abstract syntax of a model transformation, introduced in \cref{sec:dsltrans}. An example of a model transformation can be observed in \cref{fig:dsltransformation}, the Police Station transformation. As expected, a DSLTrans transformation is composed of a sequence of layers where each layer is composed of a set of rules.

\begin{definition}{Layer\\}
\label{def:layer}
A layer is a finite set of transformation rules: $\{r_0, r_1, \dots, r_n | r_i \in \textsc{Rules}\}$.

The set of all layers is denoted $\textsc{Layers}$. 
\end{definition}

Note that the order of the rules within the layer does not matter, due to the semantics of DSLTrans rule execution. As discussed in Section BLAH, these semantics ensure that rules are independent, and cannot act on the output of other rules within the same layer.

\begin{definition}{DSLTrans Transformation\\}
\label{def:transformation}

A DSLTrans transformation is a finite list of layers denoted $\{l_0, l_1, \dots, l_n | l \in \textsc{Layers}\}$. Note that the order of layers in a transformation is important.

The set of all transformations is denoted $\textsc{Transforms}$.

\subsubsection*{Input-Output Model}

To describe the semantics of a DSLTrans model transformation, we must define an \textit{input-output model} construct. This input-output model allows the representation of the initial state as well as intermediate operational states during the execution of a model transformation. These input-output models are thus the `path conditions' which represent all transformation executions through an abstraction relation. This is further discussed in Section ABSTRACTION RELATION.

The structure of a input-output model is intentionally very similar to a DSLTrans rule. There is one typed graph representing the input model and another typed graph representing the output model. As well, the construct contains a set of edges, named \emph{traceability links}, for keeping a history of which elements in the output model originated from which elements in the input model.

\begin{definition}{Input-Output Model\\}
\label{def:input_output_model}

An input-output model rule is a three-tuple $\big\langle \mathit{Input}$, $\mathit{Output}$, $\mathit{trace}\big\rangle$, where:

\begin{itemize}
\item $\mathit{Input}, \mathit{Output} \in \textsc{TG}$
\item $\mathit{Input}$ and $\mathit{Output} $ may be empty and are disjoint
\item $\mathit{trace} = \{E_{trace}, (s_{trace}, t_{trace})\}$
\begin{itemize}
\item $E_{trace}$ contains the traceability links
\item $E_{trace} $ is disjoint from $E_{Input}$ and $E_{Output}$
\item $(s_{trace}, t_{trace})$ is a pair of functions $s_{trace}: E_{trace}\rightarrow V_{\textit{Output}}$ and $t_{trace}: E_{trace}\rightarrow V_{\textit{Input}}$ that respectively provide the source and target vertices for each traceability link
\end{itemize}

\end{itemize}

Let $\mathit{IOM}$ be the set of all input-output models.

We define a utility function getTransformation: IOM $\rightarrow$ Transforms. This function returns the Transform that the input-output model was built for. The purpose of this function is to restrict input-output models to only be applicable for the transformation they represent.

Note that the $\VT$ and $\ET$ for input and output will come from the input and output metamodels. \bentley{Expand}

\subsection{Transformation Semantics}
\label{sec:DSLTrans_semantics}

This section will discuss the semantics of a DSLTrans transformation. Given an input model and a transformation, an output layer will be produced through the repeated execution of rules and layers.

\subsubsection*{Execution of a DSLTrans Rule}

We will now address the execution of a rule in the DSLTrans language, basing our explanation on double pushouts.

Note that we will apply rules differently, depending on whether they contain indirect links or not. We will begin with the simpler case where the rule does not contain indirect links, diagrammed in Figure~\ref{fig:dpo}.

We create first the matcher and the rewriter for a DSLTrans rule.

\subsubsection*{Matcher of a Transformation Rule}

To create the actual matcher construct that will be matched during a rule's execution, the rule's \textit{Match} graph is combined with backward links, as well as any \textit{Apply} vertices connected to the backward links.

Note that the rule's NAC will also be considered in the matching of a rule.

\begin{definition}{Matcher of a Transformation Rule\\}
\label{def:matcher_transformation_rule}

Let the transformation rule $r = \big\langle \mathit{NAC}$, $\mathit{Match}$, $\mathit{Apply}$, $\mathit{backward}\big\rangle$.

We define $r$'s matcher, noted $\lceil r \rceil$, to be a typed graph six-tuple $\langle V,E,(s,t),\tau, \VT, \ET\rangle$, where:
\begin{itemize}
\item $V = V_{Match} \cup \big\{v \in V_{Apply} | \{\exists e \in E_{back} | s_{back}(e) = v\}\big\}$
\item $E = E_{Match} \cup E_{back}$
\item $s = s_{Match} \cup s_{back}$, $t = t_{Match} \cup t_{back}$
\item $\tau = \tau_{Match} \cup \tau_{Apply}$
\item $\VT = \VT_{Match} \cup \VT_{Apply}$
\item $\ET = \ET_{Match} \cup \ET_{Apply}$
\end{itemize}

\subsubsection*{Rewriter of a Transformation Rule}

To continue with the double pushout approach, we must construct the rewriting (or replacement) graph.

The construction of this rewriter is essentially the same as the underlying rule. However, to support traceability, we require that backward links in the rule be converted into traceability links, and that new traceability links be created between all match and apply vertices.

\begin{definition}{Rewriter of a Transformation Rule\\}
\label{def:rewriter_transformation_rule}

Let the transformation rule $r = \big\langle \mathit{NAC}$, $\mathit{Match}$, $\mathit{Apply}$, $\mathit{backward}\big\rangle$.

We define $r$'s rewriter, noted $\lfloor r \rfloor$, to be a structure $\big\langle \mathit{Input}$, $\mathit{Output}$, $\mathit{trace}\big\rangle$, where:

\begin{itemize}
\item $ \mathit{Input} = \mathit{Match}$
\item $ \mathit{Output} = \mathit{Apply}$
\end{itemize}

We then modify $\mathit{trace}$ to contain the appropriate traceability links

\begin{itemize}
\item $E_{trace} = \exists e \in E_{trace} | $
\begin{itemize}
\item $ \forall m \in V_{Match}, a \in V_{Apply}:$$s_{trace}(e) = a$, $t_{trace}(e) = m$ 
\end{itemize}
\end{itemize}

\subsubsection*{Double-pushout Approach}

\begin{figure}[h!] \centering
\includegraphics[width=0.44\textwidth]{figures/formal/dpo}
	\caption{Double pushout approach}
	\label{fig:dpo}
\end{figure}

We explain the components:
\begin{itemize}
\item L: The matcher of the rule
\item R: The rewriter of the rule
\item G: The graph to be matched/rewritten
\item H: The rewritten graph
\end{itemize}

Note that as it is not possible in DSLTrans rules to remove elements, in this case $L = K$, and $G = D$.

\bentley{Fix up morphism notation. Is $\rightarrow$ good enough?} 
Recall that the interface graph K is equivalent to L due to the lack of deletion in DSLTrans rules. Thus, the l homomorphism is identity. The D correspondence graph will therefore be equivalent to G.

As well, we consider r to be a trivial homomorphism between the $\mathit{Match} \rightarrow \mathit{Input}$, $\mathit{Apply} \rightarrow \mathit{Output}$, and $\mathit{backward} \rightarrow \mathit{trace}$.

We also note here that a rule cannot be applied if there is a homomorphism between the rule's NAC and G.

m is the typed graph homomorphism between the matcher of a rule $r$, denoted ($\lceil r \rceil$) and the $\mathit{Input}$ component of the input-output model

$n$ and $g$ will be homomorphism between their respective graphs. \bentley{This needs to be explained further. Maybe with a diagram?}

\subsubsection*{DSLTrans Layer Execution}

Now that the application of a particular DSLTrans rule has been explained, the next definition defines how a DSLTrans transformation layer executes. Recall that a layer is composed of rules, and acts on the current input-output model.

\begin{definition} {DSLTrans Layer Execution}
\label{def:dsltrans_layer_execution}

The execution of a DSLTrans layer can be defined as a function as follows:

\textit{applyLayer} : IOM $\times$ Layer $\rightarrow$ IOM

Let $l = \{r_0, r_1, \dots, r_n | r_i \in \textsc{Rules}\}$, $l \in \textsc{Layers}$.

Let $\mathit{IOM}_{Input}$, $\mathit{IOM}_{Output} \in \mathit{IOMs}$.

$\mathit{IOM}_{Output}$ will be the result of applying the production \textit{p} as defined below to $\mathit{IOM}_{Input}.$

We refer to the double-pushout literature for the creation of \textit{p}. Specifically, we refer to the definition of parallel direct derivations. This p will be created out of the productions created for each of the rules $r_i$ in the layer.

$p = \big\langle (p_1, {in}^1), \dots, (p_k, {in}^k) \big\rangle : (L \xleftarrow{l} L \xrightarrow{r} R)$

This collection of the rules is possible because DSLTrans rules do not delete anything. Essentially, a union is taken of the L, K, R components of each production.
\end{definition}

\begin{figure}[h!] \centering
\includegraphics[width=0.44\textwidth]{figures/formal/parallel_productions}
	\caption{Parallel production \textit{p}}
	\label{fig:parallel_productions}
\end{figure}

\cref{def:dsltrans_layer_execution} is the core of DSLTrans' semantics, in which we build the result of executing a layer of a DSLTrans transformation. Many model transformation languages are based on graph rewriting, where the result of each rule rewrite is immediately usable by all other rules. In DSLTrans the result of executing one layer in DSLTrans is totally produced before the input to the layer is changed. This is enforced in \cref{def:dsltrans_layer_execution} by the fact that the layer production is composed of a union of the rule's productions. Rules belonging to the same layer are thus forced to execute independently, as described in the section on DSLTrans semantics.

\bentley{How does this handle different multiplicity of rule application?}

\subsubsection*{DSLTrans Transformation Execution}

Our final definition is for the execution of a DSLTrans transformation. Essentially, it is the chaining of layer executions applied on an input-output model.

We will begin by discussing the conditions for executing a model transformation on an input model.

\paragraph{Input Conditions}

For a well-formed transformation execution, we require the \textit{input-output model} in the domain to contain only an input graph. Recall that an \textit{input-output model} is the three-tuple $\big\langle \mathit{Input}$, $\mathit{Output}$, $\mathit{trace}\big\rangle$. We therefore require that both the $\mathit{Output}$ and $\mathit{trace}$ components in the domain IOM to be empty. This input-output model thus represents the first step of the transformation, where no rule has been executed yet.

The input-output model in the co-domain will contain this input graph, as well as the output graph and traceability links produced by the execution of the transformation. Let $\textsc{Execs}_t$ be the set of all well-formed input-output models produced for transformation $t$.

\begin{definition} {Execution of a DSLTrans Transformation\\}
\label{def:DSLTrans_transformation_execution}

The execution of a model transformation is a function $\mathit{applyTransformation}: \mathit{IOM} \times \mathit{Transforms} \rightarrow \mathit{IOM}$.

This function is a chaining of executions of those layers within the transformation.

Recall the application of a layer is \textit{applyLayer} : IOM $\times$ Layer $\rightarrow$ IOM. Therefore, the application of a transformation is:

$\mathit{IOM}$ as input to chaining of layer executions \bentley{Is this function chaining? I don't know how to write the equation for this.}

While the execution of the rules belonging to a layer happens in parallel, the execution of the layers of a transformation happens sequentially. As per \cref{def:DSLTrans_transformation_execution}, the input-output model that is the output of executing a given layer is passed onto the next layer as input. The final input-output model created will be the result of the model transformation.

\subsection{Confluence and Termination Properties}

We now prove two important properties about executions of transformations expressed in the subset of DSLTrans presented in this paper: \emph{confluence} and \emph{termination}. The proofs are provided at a high level, given the fact that DSLTrans essentially enforces both these properties by construction of the semantics of DSLTrans.

\begin{proposition}{Confluence}

Every model transformation execution is confluent up to typed graph isomorphism.

\bentley{As we are relying on the double-pushout approach, I think we get this confluence for free.}

\end{proposition}

\begin{pf}
We want to prove that for every model transformation execution of a transformation $\mathit{transform} \in \textsc{Transforms}$ having as input an input-output model $\mathit{input} \in \mathit{IOMs}$, its output is always the same up to typed graph isomorphism.\\

If we assume an execution of the transformation is not confluent then this should happen because of non-determinism when the execution of a transformation is being built. Non-determinism happens during the construction of a transformation execution at two points: 
\begin{enumerate}
\item The section `Execution of a DSLTrans Rule' discusses the matching and rewriting components to rule application. Note that our technique relies on the double-pushout approach, which itself is non-deterministic up to typed graph isomorphism, which does not contradict the proposition we are trying to prove. \bentley{Revise this.}

\item In Definition~\ref{def:dsltrans_layer_execution}, the rules composing a transformation layer are composed into a production on the input graph. Note that the order in which the transformation rules are composed may be non-deterministic. However, as these rules can be shown to be parallel independent \bentley{And they have to in that definition}, the production is by definition confluent up to typed graph isomorphism.

\end{enumerate}
Given there are no other sources of non-determinism when building the execution of a transformation, every model transformation execution is confluent up to typed graph isomorphism.
\end{pf}

\begin{proposition}{Termination}

Every model transformation execution terminates.
\end{proposition}
\begin{pf}
Let us assume that there is a transformation execution which does not terminate. In order for this to happen there must exist a part in the construction of the execution of a transformation which induces an algorithm with an infinite amount of steps. We identify three moments when this can happen:
\begin{enumerate}

\item If the matching and rewriting process of a rule is infinite. However, as the double-pushout approach uses a single production, then this must be a finite process. \bentley{Verify this, especially in the case of multiple applications of the rule.}

% if the result of the $match_{rl}(m_{in})$ function in definition~\ref{def:match_function} is an infinite set of match-apply graphs. The input-output model $m_{in}$ is by definition finite and the matching of each rule is independent from the execution of other rules in the same layer. As such, the number of subgraphs of $m_{in}$ isomorphic to $rl$'s matcher found during the execution of $rl$ is finite.

\item if Definition~\ref{def:dsltrans_layer_execution} of execution of a layer induces an infinite amount of steps. The only possibility for this to happen is if a layer has an infinite amount of transformation rules, which is a contradiction with Definition~\ref{def:layer}.

\item if Definition~\ref{def:DSLTrans_transformation_execution} of execution of a transformation induces an infinite amount of steps. Given layers are executed sequentially and no looping is allowed, the only possibility for this to happen is if the transformation has an infinite amount of layers, which contradicts Definition~\ref{def:transformation}.

\end{enumerate}
Given there are no other constructs in the semantics of a transformation that can induce an infinite amount of steps, every model transformation execution terminates.
\end{pf}

>>>>

@@

\subsubsection{Homomorphisms Between Structures}
\label{subsubsec:structure_homomorphism}

In the developments that follow, we will need to find morphisms between different structures.

For example, we may need to find a homomorphism between two structures $S_1 = \langle A, B, L\rangle$ and  $S_2 = \langle A', B', L'\rangle$, where $A, A', B, B' \in TG$ and $L, L'$ are links of the form $\{E, (s, t)\}$.

This overall homomorphism will compose the homomorphism $f(A) = A'$, $g(B) = B'$, $h(L) = L'$, where f and g are the homomorphisms to be found, and h is the link homomorphism.

A reviewer pointed out that we also require that these sub-homomorphisms are consistent with each other. That is, the link homomorphism h must agree with 
the bindings given by f and g.

\bentley{Complete this}

### 2016-07-29 text/implementation.tex
Add reviewer's comments into the paper.
Replace DSLTrans section with Frankenstein from different sources.

@@

\begin{figure*}[htb]
        \centering
        \begin{subfigure}[b]{0.26\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/results/rules_vs_pcs.pdf}
                \caption{Number of rules vs. \\path conds. created}
                \label{fig:rules_vs_pcs}
        \end{subfigure}%
        ~~
        \begin{subfigure}[b]{0.26\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/results/rules_vs_time.pdf}
                \caption{Number of rules vs. \\time taken}
                \label{fig:rules_vs_time}
        \end{subfigure}%
        ~~
        \begin{subfigure}[b]{0.26\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/results/rules_vs_memory.pdf}
                \caption{Number of rules vs. \\memory used}
                \label{fig:rules_vs_memory}
        \end{subfigure}%

        \caption{Metrics for the path condition creation process}
        \label{fig:path_condition_building}
\end{figure*}

>>>>

\reviewer{Table 1, even if it was not experimented to exceed 0.003 seconds when proving for property that does not hold, maybe it would be possible to estimate the maximum time based on that measurement and the complexity formula.}

@@

%\begin{figure*}[htb]
%        \centering
%        \begin{subfigure}[b]{0.26\textwidth}
%                \centering
%                \includegraphics[width=1\textwidth]{./figures/results/rules_vs_pcs.pdf}
%                \caption{Number of rules vs. \\path conds. created}
%                \label{fig:rules_vs_pcs}
%        \end{subfigure}%
%        ~~
%        \begin{subfigure}[b]{0.26\textwidth}
%                \centering
%                \includegraphics[width=1\textwidth]{./figures/results/rules_vs_time.pdf}
%                \caption{Number of rules vs. \\time taken}
%                \label{fig:rules_vs_time}
%        \end{subfigure}%
%        ~~
%        \begin{subfigure}[b]{0.26\textwidth}
%                \centering
%                \includegraphics[width=1\textwidth]{./figures/results/rules_vs_memory.pdf}
%                \caption{Number of rules vs. \\memory used}
%                \label{fig:rules_vs_memory}
%        \end{subfigure}%
%
%        \caption{Metrics for the path condition creation process}
%        \label{fig:path_condition_building}
%\end{figure*}

### 2016-07-29 text/property_verification.tex
Add more on homomorphisms.
Update with some work-in-progress for abstraction relation.
Replace DSLTrans section with Frankenstein from different sources.

\begin{figure}[htb]
        \centering
        \begin{subfigure}[b]{0.40\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/property_proving/prop_execution_without_traceability.pdf}
                \caption{Property holds}
                \label{fig:prop_execution_without_traceability}
        \end{subfigure}%
        \\
        \begin{subfigure}[b]{0.40\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/property_proving/prop_execution_with_traceability.pdf}
                \caption{Property does not hold}
                \label{fig:prop_execution_with_traceability}
        \end{subfigure}%
        \caption{Matching property to a transformation execution}
        \label{fig:prop_execution}
\end{figure}

@@

\begin{figure}[htb]
        \centering
        \begin{subfigure}[b]{0.144\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/property_proving/unprovable_rule.pdf}
                \caption{Path condition created from a rule}
                \label{fig:unprovable_pc}
        \end{subfigure}%
        ~~
        \begin{subfigure}[b]{0.20\textwidth}
                \centering
                \includegraphics[width=1\textwidth]{./figures/property_proving/unprovable_prop.pdf}
                \caption{Property with multiple instances of rule elements}
                \label{fig:unprovable_prop}
        \end{subfigure}%
        \caption{Example of unprovable property}
        \label{fig:unprovable_property}
\end{figure}

>>>>

%\begin{figure}[htb]
%        \centering
%        \begin{subfigure}[b]{0.40\textwidth}
%                \centering
%                \includegraphics[width=1\textwidth]{./figures/property_proving/prop_execution_without_traceability.pdf}
%                \caption{Property holds}
%                \label{fig:prop_execution_without_traceability}
%        \end{subfigure}%
%        \\
%        \begin{subfigure}[b]{0.40\textwidth}
%                \centering
%                \includegraphics[width=1\textwidth]{./figures/property_proving/prop_execution_with_traceability.pdf}
%                \caption{Property does not hold}
%                \label{fig:prop_execution_with_traceability}
%        \end{subfigure}%
%        \caption{Matching property to a transformation execution}
%        \label{fig:prop_execution}
%\end{figure}

@@

%\begin{figure}[htb]
%        \centering
%        \begin{subfigure}[b]{0.144\textwidth}
%                \centering
%                \includegraphics[width=1\textwidth]{./figures/property_proving/unprovable_rule.pdf}
%                \caption{Path condition created from a rule}
%                \label{fig:unprovable_pc}
%        \end{subfigure}%
%        ~~
%        \begin{subfigure}[b]{0.20\textwidth}
%                \centering
%                \includegraphics[width=1\textwidth]{./figures/property_proving/unprovable_prop.pdf}
%                \caption{Property with multiple instances of rule elements}
%                \label{fig:unprovable_prop}
%        \end{subfigure}%
%        \caption{Example of unprovable property}
%        \label{fig:unprovable_property}
%\end{figure}
